### 2014-07-29 paper/paper.tex
Wrote a section explaing the use of the validation set and a section for futre work

The Maximum Entropy classification method that was focused on due to the
limited duration of the project. This supervised machine learning method
calculates the probability that a given document $d$ belongs to the class $c$.

The maximum entropy approach is well described in \cite{Nigam1999} and is
summarized below. The training data is used to establish constraints in the
following fashion.

\begin{equation}
    P(c | d) = \frac{1}{Z(d)} exp( \sum\limits_{i} \lambda _{i,c} F_{i,c}(d,c) )
\end{equation}

@@

In order to establish reasonable $\lambda_{i}$ for each feature the Improved
Iterative Scaling is employed.

%TODO outline the IIS algorithm

@@

    \item \textbf{Training} -

    \item \textbf{Testing} - The performance of the dataset is evaulated
        against the \textit{testing set}.

@@

@@

\section{Works Cited}

>>>>

The Maximum Entropy classification method that was focused on due to the
limited duration of the project. This supervised machine learning method
calculates the probability that a given document $d$ belongs to the class $c$. The maximum entropy approach is well described in \cite{Nigam1999} and is summarized below.

The training data is used to establish constraints in the following fashion.

\begin{equation}
    P(c | d) = \frac{1}{Z(d)} \mathrm{exp}(\sum\limits_{i} \lambda _{i,c} F_{i,c}(d,c) )
\end{equation}

@@

In order to establish reasonable $\lambda_{i}$ for each feature the Improved
Iterative Scaling (IIS) is employed. Given a set of training data
$\mathcal{D}$, IIS trains a model $\Lambda$ by performing a hillclimbing procedure with the function $l(\Lambda|\mathcal{D})$, where:

\begin{equation}
    l(\Lambda | \mathcal{D}) = \sum\limits_{d\in\mathcal{D}} \sum\limits_{i}
    \lambda_{i} f_{i}(d,c(d)) - \sum\limits_{d\in\mathcal{D}} \mathrm{log}
    \sum\limits_{c} \mathrm{exp} \sum\limits_{i} \lambda_{i} f_{i}(d,c)
\end{equation}

Starting with any initial vector of parameters $\Lambda$, at each iteration
we improve the parameters by setting $\Lambda = \Lambda + \Delta$.

@@

    \item \textbf{Training} - The classifier is trained using the
        \textit{training set}.  The classifier uses the \textit{validation set}
        to evaluate the training process and attempt to curtail overfitting.

    \item \textbf{Testing} - The performance of the dataset is evaluated
        against the \textit{testing set}.

@@

\subsection{Baseline}

\subsection{Avoiding overfitting}

The implementation created for this project used a validation set during
training as the primary mechanism to avoid overfitting. While training the
effectiveness of the classifier was evaluated after every iteration, using the
accuracy or F-positive measure. During the training process the following
procedure was followed:

    \item The classifier was trained for 5 iterations to establish reasonable
        initial weights.

    \item Evaluate the classifier using the validation set. Like the
        \textit{testing set} that will evaluate the classifiers final
        performance, the \textit{validation set} shares no common examples with
        the \textit{training set} and will therefore give a reasonable
        indication of how the classifier will perform with unseen examples.

    \item Repeat the following until performance degrades for a specified
        number of iterations

        \item Train the classifier for another iteration.

        \item Evaluate performance with the \textit{validation set}.

    \item Restore the $\Lambda$ value of the best performing iteration.

@@

\subsection{Hashtags}

\subsection{Users}

Nearly all Twitter users have published more than one tweet. A more advanced
classifier could establish a particular users propensity to publishing a
prevailing sentiment in all of their tweets.

As well, some Twitter users may be frequently be referred to with a particular
sentiment. For a hypothetical example, Tweets addresses to Emma Watson
(`@EmWatson') are more likely to have a positive sentiment, while tweets to
Barack Obama (`@BarackObama') may contain extremely mixed sentiment.

% Bibliography
